\documentclass[11pt]{article}
%\usepackage{}
\usepackage{a4}
\usepackage{palatino}
\usepackage[latin1]{inputenc}
\parindent0ex
\pagestyle{empty}
\begin{document}
{\large
Software License Agreement between
\begin{center}
Konrad-Zuse-Institut für Informationstechnik\\
Takustraße 7, 14195 Berlin-Dahlen, Germany\\
\end{center}
subsequently referred to as ZIB and 
\begin{center}
Monterey Design Systems\\
2171 Landings Drive, Mountain View, CA 94043, USA\\
\end{center}
subsequently referred to as Licensee,\\
about the software SoPlex, subsequently referred to as Software.
}

%\item The Licensee has the right to make up to 10 copies
%  of the Software for internal software development use. 
  
\begin{enumerate}

\item ZIB grants to the Licensee a perpetual, worldwide, non-terminable,
  irrevocable, non-exclusive license to use and distribute 
  7 (seven) copies of the Software in binary form linked to a product 
  of the Licensee called Dolphin,
  provided that the customers of the Licensee already have a license
  to the Dolphin product as of 1st of October 2004.

%the distributed product provides features or
%  functionality beyond those provided by the Software on a stand-alone
%  basis and provided that the distribution

%\item This license is also valid for all subsequent versions of the
%  Software that are optainable from ZIB's website under the 
%  ZIB Academic License.

\item The Software is delivered AS IS;
   without any warranty, neither expressed nor implied.

\item Hereby the Licensee confirms that the Software was received 
  complete and according to the Agreement.

\item The ownership of the Software remains at ZIB.

\item The copyright of the Software remains at ZIB. 

\item ZIB does not take any liabilites for damages of any kind that
  result from using the Software.

\item The Licensee pays for the license to distribute the Software 
  under the conditions noted herein a price of \$~7000.---.

\item In the event that any provision of this Agreement should be
  found by a court of competent jurisdiction to be invalid, illegal or
  unenforcable in any resprect, the validity, legality and
  enforceability of the remaining provisions contained shall not in
  any way be affected or impared thereby.
   
\item This Agreement shall be governed by the substantive and
  procedural laws of Germany. 
%Any action at law or in equity arising
%  out of or relating to this Agreement shall be filed only in the
%  courts located in Berlin, Germany. The parties hereby consent and
%  submit to the personal jurisdiction of such courts for the purposes
%  of litigating any such action.

\end{enumerate}

\bigskip
\begin{minipage}{6cm}
Berlin, \ldots\ldots\ldots

\bigskip
Henry Thieme\\                        
Director of Administration\\
ZIB
\end{minipage}
\hfill
\begin{minipage}{5cm}
Mountain View, \ldots\ldots\ldots

\bigskip
Corinne Bordelon\\
Monterey Design Systems
\end{minipage}
\end{document}

