\documentclass[11pt]{article}
%\usepackage{}
\usepackage{a4}
\usepackage{palatino}
%\usepackage[latin1]{inputenc}
\parindent0ex
\pagestyle{empty}
\begin{document}
{\large
Software License Agreement between
\begin{center}
Konrad-Zuse-Institut für Informationstechnik\\
Takustraße 7, 14195 Berlin-Dahlen, Germany\\
\end{center}
subsequently referred to as ZIB and 
\begin{center}
Sitius Automation\\
141 McPherson Street, Markham, L3R 3L3, Canada\\
\end{center}
subsequently referred to as Licensee,\\
about the software SoPlex, subsequently referred to as Software.
}

%\item The Licensee has the right to make up to 10 copies
%  of the Software for internal software development use. 
  
\begin{enumerate}

\item ZIB grants to the Licensee a perpetual, worldwide, non-terminable,
  irrevocable, non-exclusive license to use and distribute one copy of
  the Software in binary form linked to a product of the Licensee,
  provided that the distributed product provides features or
  functionality beyond those provided by the Software on a stand-alone
  basis.

\item This License is also valid for all subsequent versions of the
  Software that are optainable from the ZIB website under the 
  ZIB Academic License.

\item The Software is delivered AS IS;
   without any warranty, neither expressed nor implied.

\item Hereby the Licensee confirms that he has received the Software 
  complete and according to the agreement.

\item The Ownership of the Software remains at ZIB.

\item The Copyright of the Software remains at ZIB. 

\item ZIB does not take any liabilites for damages of any kind that
  result from using the Software.

\item The licensee pays for this license the amount of US~\$~100.---

\item Subject to the terms and conditions applicable to a single copy
  of the licensed software, the Licensee will have the option to
  purchase a volume license for the rights to distribute (50) copies
  of the software for the price of US\$~2,500.

\item The Licensee has the option to buy a license for the
  distribution of an Unlimited
  number of copies of the software for the price of US\$~5,000. 
  The details and restrictions for the unlimited license are subject
  to another license agreement.
  
\item The price structure outlined in this agreement will be
  maintained until 12/31/2005. After this the parties may decide to
  renew the agreement under the same or modified financial terms.
   
\item This Agreement shall be governed by the substantive and
  procedural laws of Germany. Any action at law or in equity arising
  out of or relating to this Agreement shall be filed only in the
  courts located in Berlin, Germany. The parties hereby consent and
  submit to the personal jurisdiction of such courts for the purposes
  of litigating any such action.

\end{enumerate}

\bigskip
\begin{minipage}{4cm}
Berlin, the ..........

\bigskip
Henry Thieme\\                        
Verwaltungsleiter ZIB
\end{minipage}
\hfill
\begin{minipage}{4cm}
Markham, the ........

\bigskip
George Kovatchev\\
Sitius Automatation
\end{minipage}
\end{document}

